GeckoGraph: A Visual Language for Polymorphic Types

### 2025-04-04 main.tex
Some changes in eval

The level 10 is the most cognatively taxing: the provided functions are very long and complex, and the solution is very challenging and deceptive, programmers have to utilize all the provided functions, and compese them eight time to reach the final position. Because level 10 require programmers to switch back and forth to remember what each function does. We speculate that this level require the mental agility of a Haskell expert to internalize these functions, and GeckoGraph help less experienced programmers achieve the similar level efficacy.

@@

It is interesting to note that programmers find GeckoGraph intuitive, and the more experienced they are, the more likely they find GeckoGraph easy to use. We believe this aligns with our design decision to make GeckoGraph resemble text-based type annotation. Those familiar with text-based type annotation will find GeckoGraph second nature to read. However, the correlation reverses when it comes to perceived helpfulness. The more experienced the users are, the less likely they are to find GeckoGraph helpful. We speculate this pattern occurs because users who are experts in text-based type annotations naturally prefer reading text-based notation and tend to ignore GeckoGraph, diminishing its usefulness. Conversely, novice users are drawn to GeckoGraph and find its visualization offers more clarity than text-based notations.

>>>>

Level 10 is the most cognitively demanding: the provided functions are the lengthiest, and the solution is challenging and deceptive. Programmers must use the provided rotate function {\it f2} to adjust the positions of the four components of the {\it Zero} value four time to get to the correct position. Completing the level requires applying the functions {\it f1}, {\it f2}, and {\it f3} in a nested sequence that is 8 layers deep. Consequently, programmers need to frequently switch contexts to recall the purpose of each function. We speculate that this level demands the mental flexibility typical of a Haskell expert to quickly internalize these functions. GeckoGraph helps less experienced programmers to achieve the same level of comprehension fluency by adding structual clarity.

@@

Two interesting trends emerge. First, the more experienced the users are, the more likely they find GeckoGraph intuitive and easy to use. We believe this aligns with our design decision to make GeckoGraph resemble text-based type annotation. Those familiar with text-based type annotation find GeckoGraph second nature to read. Second, the correlation reverses when it comes to perceived helpfulness. The more experienced the users are, the less likely they are to find GeckoGraph helpful. We speculate this pattern occurs because users who are experts in text-based type annotations naturally prefer reading text-based notation and tend to ignore GeckoGraph, diminishing its usefulness. Conversely, novice users are more likely to be drawn to GeckoGraph and find its visualization offers more clarity and useful insights.
